Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-12 draft/accordionComplexSurfaces.tex
test

\usepackage[T1]{fontenc}
\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide, float, blkarray, chemmacros}
\usepackage{marginnote}
\hypersetup{colorlinks=true, citecolor=darkblue, linkcolor=darkblue}
\usepackage[all]{xy}
%\usepackage[bottom]{footmisc}
\usepackage{tikz}
\usepackage{tkz-graph}
\usetikzlibrary{trees, decorations, decorations.markings, shapes, arrows, matrix, calc, fit, intersections, patterns, angles}
\graphicspath{{figures/}}
\makeatletter\def\input@path{{figures/}}\makeatother
\usepackage{caption}
\captionsetup{width=\textwidth}

@@

\begin{definition}
\label{def:accordion}
A \defn{$\dissection$-accordion} is a $B$-curve~$\alpha$ of~$\bar\surface$ such that whenever~$\alpha$ meets a face~$f$~of~$\dissection$,
\begin{itemize}
\item it enters crossing an edge~$a$ of~$f$ and leaves crossing an edge~$b$ of~$f$ (in other words, $\alpha$ is not allowed to circle around~$f\dual$ when~$f\dual$ is a puncture),
\item the two edges~$a$ and~$b$ of~$f$ crossed by~$\alpha$ are consecutive along the boundary of~$f$,
\item $\alpha$, $a$ and~$b$ bound a disk inside~$f$ that does not contain~$f\dual{}$.
\end{itemize}
By convention, we also consider that the punctures of~$V\dual$ are $\dissection$-accordions; 
if we were working on the universal cover of the surface, the~$\dissection$-accordion associated to a puncture would be the infinite line crossing all (infinitely many) arcs attached to the puncture.
\end{definition}

>>>>

\usepackage[T1]{fontenc}
\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide, float, blkarray}
\usepackage{marginnote}
\hypersetup{colorlinks=true, citecolor=darkblue, linkcolor=darkblue}
\usepackage[all]{xy}
%\usepackage[bottom]{footmisc}
\usepackage{tikz}
\usepackage{tkz-graph}
\usetikzlibrary{trees, decorations, decorations.markings, shapes, arrows, matrix, calc, fit, intersections, patterns, angles}
\graphicspath{{figures/}}
\makeatletter\def\input@path{{figures/}}\makeatother
\usepackage{caption}
\captionsetup{width=\textwidth}

@@

\begin{definition}
\label{def:accordion}
A \defn{$\dissection$-accordion} is a $B$-curve~$\alpha$ of~$\bar\surface$ such that whenever~$\alpha$ meets a face~$f$~of~$\dissection$,
\begin{itemize}
\item it enters crossing an edge~$a$ of~$f$ and leaves crossing an edge~$b$ of~$f$ (in other words, $\alpha$ is not allowed to circle around~$f\dual$ when~$f\dual$ is a puncture),
\item the two edges~$a$ and~$b$ of~$f$ crossed by~$\alpha$ are consecutive along the boundary of~$f$,
\item $\alpha$, $a$ and~$b$ bound a disk inside~$f$ that does not contain~$f\dual{}$.
\end{itemize}
By convention, we also consider that the punctures of~$V\dual$ are $\dissection$-accordions.
\end{definition}
